River networks dampen long-term hydrological signals of climate change

### 2017-04-11 drafts/PNAS/Chezik_PNAS_SI.tex
Organized
Removed Lingering Defunct Files and Cleaned Up For Reproducibility.

\section*{Supplementary Information}
The following supplementary material includes 5 additional figures. Figures \ref{fig:S1} and \ref{fig:S2} are similar to figure 4 in the main text where monthly trends in flow are shown for the basin along with trend attenuation results. In these supplementary figures we highlight minimum and median flow trends rather than maximum flow trends. Figure \ref{fig:S3} demonstrates the effect of the seasonal transition of spring and fall on the climate portfolio index values within and among Fraser River sub-basins. Figures \ref{fig:S4} and \ref{fig:S5} are example plots demonstrating a single null-model iteration for the median flow metric.

@@

\begin{figure*}
\centering
\includegraphics[width=11.4cm]{FigS3_SeasonClimPort.pdf}
	\caption{Climate portfolio index by month at 55 sites within  the Fraser River basin. Lines are loess smoothers with a smoothing span of 1 to reduce noise and highlight general season shifts in climate portfolio among and across Fraser River sub-basins.}
	\label{fig:S3}
\end{figure*}

\begin{figure*}
	\includegraphics[width=17.8cm]{FigS4_SiteSim.pdf}
	\caption{Example site specific flow simulations. Annual median-flow simulations (yellow) and observations (blue) for all 55 sites considered in this study found within the Fraser River basin. Simulations at each site were parameterized using the observed data but no trend was imposed. Fifty-five site simulations equate to one basin-wide simulation. Each flow metric was simulated 1000 times basin-wide per response variable. See supplemental figure \ref{fig:S5} for resultant basin-wide simulation.}
	\label{fig:S4}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=11.4cm]{FigS5_BasinSim.pdf}
	\caption{Example flow simulation results. Trend estimates $\pm$SE of simulated null-model data (yellow) and the observed data upon which simulations were based (blue), plotted against watershed area. Curved lines represent the estimated variance function ($\hat{\updelta}$) given the simulated data. This is a single example result of the 1000 null-model simulations produced from the data in supplemental figure \ref{fig:S3}.}
	\label{fig:S5}
\end{figure*}

>>>>

\section*{Supplementary Information}
The following supplementary material includes 4 additional figures. Figures \ref{fig:S1} and \ref{fig:S2} are similar to figure 4 in the main text where monthly trends in flow are shown for the basin along with trend attenuation results. These supplementary figures highlight minimum and median seasonal flow trends rather than maximum seasonal flow trends. Figures \ref{fig:S3} and \ref{fig:S4} are example plots demonstrating a single null-model iteration for the median flow metric.

@@

\begin{figure*}
	\includegraphics[width=17.8cm]{FigS3_SiteSim.pdf}
	\caption{Example site specific flow simulations. Annual median-flow simulations (yellow) and observations (blue) for all 55 sites considered in this study found within the Fraser River basin. Simulations at each site were parameterized using the observed data but no trend was imposed. Fifty-five site simulations equate to one basin-wide simulation. Each flow metric was simulated 1000 times basin-wide per response variable. See supplemental figure \ref{fig:S5} for resultant basin-wide simulation.}
	\label{fig:S3}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=11.4cm]{FigS4_BasinSim.pdf}
	\caption{Example flow simulation results. Trend estimates $\pm$SE of simulated null-model data (yellow) and the observed data upon which simulations were based (blue), plotted against watershed area. Curved lines represent the estimated variance function ($\hat{\updelta}$) given the simulated data. This is a single example result of the 1000 null-model simulations produced from the data in supplemental figure \ref{fig:S3}.}
	\label{fig:S4}
\end{figure*}
